Restrictive Clearance Comparison

### 2024-04-04 data-raw/RestrictiveClearance_comparison.Rmd
Added a kelim comparison for "old fits" and the newer restrictive vs non-restrictive fits to diagnose an issue with fitting algorithm.

```{r running-invivoPKfit}
minimal_pk <- pk(data = cvt %>%
                   filter(analyte_dtxsid %in% unique(combined_clearance_df$Chemical)),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = dose_level_normalized,
                   Dose.Units = "mg/kg",
                   Subject_ID = subject_id,
                   Series_ID = series_id,
                   Study_ID = study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_in_series,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = conc,
                   Value.Units = "mg/L",
                   Value_SD = conc_sd_normalized,
                   LOQ = loq
                 ))

@@

>>>>

```{r running-invivoPKfit}
minimal_pk <- pk(data = cvt %>%
                   filter(analyte_dtxsid %in% "DTXSID0020442"),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = dose_level_normalized,
                   Dose.Units = "mg/kg",
                   Subject_ID = subject_id,
                   Series_ID = series_id,
                   Study_ID = study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_in_series,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = conc,
                   Value.Units = "mg/L",
                   Value_SD = conc_sd_normalized,
                   LOQ = loq
                 ))

@@

Why are so many fits failing?
Well, we should take a look at the parameter which we are holding constant,
`kelim` and whether the new starting points vastly differ from those in the
starting points based on the data.

For this I will just use the PK object I have saved `my_pk` and take the
_prefit_ parameter estimations and first compare that with eventual optimized `kelim`.

```{r kelim-questions}

# Original data, filtered for common_chems
# par_DF
my_kelim_prefit <- my_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim",
         Chemical %in% common_chems) %>%
  distinct(Chemical, Species, param_name, lower_bound, upper_bound, start)

my_kelim_fit <- coef(my_pk) %>%
  inner_join(get_winning_model(my_pk)) %>%
  ungroup() %>%
  distinct(model, Chemical, Species, kelim) %>%
  rename(fit_kelim = "kelim") %>%
  filter(Chemical %in% common_chems)

my_kelim_df <- inner_join(my_kelim_fit, my_kelim_prefit)

httk_df <- rest_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_restrictive = "start") %>%
  inner_join(
    nonrest_pk$prefit$par_DF %>%
  filter(param_name %in% "kelim") %>%
  distinct(Chemical, Species, param_name, start) %>%
  rename(init_nonrestrictive = "start"))

full_df <- inner_join(my_kelim_df, httk_df) %>%
  relocate(fit_kelim, .after = last_col())

full_df %>%
  ggplot(aes(x = Chemical)) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "grey30") +
  geom_errorbar(aes(ymax = upper_bound, ymin = lower_bound)) +
  geom_point(aes(y = fit_kelim, color = "Original Optimized")) +
  geom_point(aes(y = init_restrictive, color = "Restrictive")) +
  geom_point(aes(y = init_nonrestrictive, color = "Non-restrictive")) +
  geom_point(aes(y = start, shape = "Original Initialized")) +
  facet_grid(rows = vars(Species), scales = "free", space = "free") +
  scale_color_manual(name = "kelim",
                     breaks = c("Original Optimized", "Restrictive", "Non-restrictive"),
                     values = c("Original Optimized" = "skyblue4", 
                                "Restrictive" = "orange2",
                                "Non-restrictive" = "green4")) +
  scale_shape_manual(name = "",
                     values = 4) +
  coord_flip() +
  scale_y_log10(labels = scales::label_math(format = log10)) +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1.5),
        panel.background = element_blank(),
        panel.grid.major = element_line(color = "grey90", linewidth = 0.5),
        strip.background = element_rect(fill = "white"),
        strip.text = element_text(face = "bold"),
        legend.direction = "vertical",
        axis.ticks = element_blank(),
        axis.line = element_blank(),
        axis.text.y = element_blank(),
        strip.text.y = element_text(angle = 0))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"), "kelim_compare_2024_0329.png"),
       height = 11,
       width = 8.5)
```

```{r testing_optimx}
test_optimx <- do.call(
          optimx::optimx,
          args = c(
            list(par = opt_params,
                 fn = log_likelihood,
                 lower = lower_params,
                 upper = upper_params),
            #method and control
            settings_optimx,
            #... additional args to log_likelihood
            list(
              const_params = const_params,
              data = data,
              data_sigma_group = data$data_sigma_group,
              modelfun = modelfun,
              dose_norm = dose_norm,
              log10_trans = log10_trans,
              negative = TRUE,
              force_finite = TRUE,
              suppress.messages = FALSE
            ) #end list()
          ) #end args = c()
        ) #end do.call
```

```{r}
